---
title: "Anlysis of Marriage Licenses Issued between 2011 to 2024"
author: 
  - Aakash Vaithyanathan
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Study of marriage license issued by month between the month of 2011 and 2024 for various provinces in Canada."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

We use @R, @ggplot2, and @opendatatoronto in this project.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}
```{r}
#| label: fig-marriage
#| fig-cap: Number of Marriage Licences Issued by Month
#| echo: false

data |> 
  ggplot(aes(x = month, y = marriage_licenses)) +
  geom_bar(stat="identity") +
  ggtitle("Bar plot of marriage licenses issued from 2011 to 2024 by Month") +
  xlab("Month") +
  ylab("Total Marriage Licences Issued")

```


# Discussion
The above graph was generated using data from @R, @ggplot2, and @opendatatoronto. The graph shows the total number of issued marriage licences between the years of 2021 and 2024 for every month.
## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References

